Tool-driven Revolutions in Archaeological Science

### 2019-08-09 analysis/paper/jcaa-paper.Rmd
typo.

---
title: "Tool-driven Revolutions in Archaeological Science"
author:
  - author 1
  - author 2
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
bibliography: references.bib
csl: journal-of-computer-applications-in-archaeology.csl
abstract: "There is an argument in philosophy of science that revolutions in science are either ideas-driven or tools-driven. We explore this debate in light of recent efforts by many scientific disciplines to embrace methods to improve the reproducibility of their research. One of the most profound changes driven by this concern for reproducibility and transparency is from using data analysis tools dependent on point-and-clicking with a mouse in closed source software, to a set of tools based on writing scripts in open source programming languages and making the scripts openly available. We present bibliometric evidence for this change in ecolpogy and archaeology to test if the adoption of these new tools may be considered a revolution. We identify a citation effect for archaeology articles that use the open source programming language R. We discuss how computational approaches to improving reproducibility and transparency in archaeology are mediated and transformed by the use of R code."
---

>>>>

---
title: "Tool-driven Revolutions in Archaeological Science"
author:
  - author 1
  - author 2
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
bibliography: references.bib
csl: journal-of-computer-applications-in-archaeology.csl
abstract: "There is an argument in philosophy of science that revolutions in science are either ideas-driven or tools-driven. We explore this debate in light of recent efforts by many scientific disciplines to embrace methods to improve the reproducibility of their research. One of the most profound changes driven by this concern for reproducibility and transparency is from using data analysis tools dependent on point-and-clicking with a mouse in closed source software, to a set of tools based on writing scripts in open source programming languages and making the scripts openly available. We present bibliometric evidence for this change in ecology and archaeology to test if the adoption of these new tools may be considered a revolution. We identify a citation effect for archaeology articles that use the open source programming language R. We discuss how computational approaches to improving reproducibility and transparency in archaeology are mediated and transformed by the use of R code."
---
